---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SummaryStats

<!-- badges: start -->
<!-- badges: end -->

**SummaryStats** is an R package that provides a function to calculate summary statistics (mean, median, and count) for a specified numeric column within a data frame, grouped by one or more categorical columns.  


## Installation


To install the development version of **SummaryStats** directly from GitHub, you'll need the `devtools` package:

```{r}
install.packages("devtools")
```

Then, use the following command:

```{r}
devtools::install_github("ManiSadati/SummaryStats", ref = "0.1.0")
```




## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(datateachr) # <- might contain the data you picked!
library(tidyverse)
library(testthat)
library(SummaryStats)

# Sample data
data <- data.frame(
  category = c("A", "A", "B", "B"),
  values = c(10, 20, 30, 40)
)

# Calculate summary statistics
summary_result <- SummaryStats(data, group_vars = "category", summary_var = "values")

# View the results
summary_result
```

